Measurement and Probability in Fuzzy Quantum Theories

### 2017-06-11 prop_iop.tex
prop_iop.tex \subsection{From Real-valued to Interval-valued} Updating..

Notice that the range of $\mu$ and $\bar{\mu}$ are different. If
there is a good function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$,
then a QIVPM can be easily defined by function composition\nb$\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$.
This gives the following definition.

\begin{definition}We say a pair\nb$\left(\mathscr{I},\iota\right)$
is additive\footnote{\yutsung{This whole definition might be rewritten using category
theory... I would investigate it if it is necessary...}} if $\mathscr{I}$ is a collection of intervals and $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
is a function satisfying the following properties. 
\begin{itemize}
\item $\iota\left(0\right)=\left[0,0\right]$. 
\item $\iota\left(1\right)=\left[1,1\right]$. 
\item For any $x\in\left[0,1\right]$, $\iota\left(1-x\right)=\left[1,1\right]-\iota\left(x\right)$. 
\item For a set\nb$\left\{ x_{i}\right\} _{i=1}^{N}\subseteq\left[0,1\right]$,
if $\sum_{i=1}^{N}x_{i}\in\left[0,1\right]$, then $\iota\left(\sum_{i=1}^{N}x_{i}\right)\subseteq\sum_{i=1}^{N}\iota\left(x_{i}\right)$. 
\end{itemize}
Moreover, $\left(\mathscr{I},\iota\right)$ is called convex if for
any three numbers\nb$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$,
if $x_{0}+x_{1}+x_{2}\in\left[0,1\right]$, then $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\subseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.\end{definition}

Although a convex pair\nb$\left(\mathscr{I},\iota\right)$ may look
exotic, the left end of $\iota$, defined by $\iotal\left(x\right)=\min\iota\left(x\right)$,
is the well-studied Wright-convex satisfying $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$\nb\cite{Wright1954,RobertsVarberg1973,Pales2013}.
After we define\nb$\left(\mathscr{I},\iota\right)$, we are ready
to construct a QIVPM from a quantum probability measure.

@@

\begin{proof}~
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\iota\left(\mu(\mathbb{0})\right)=\iota\left(0\right)=\left[0,0\right]$.
\item $\bar{\mu}(\mathbb{1})=\iota\left(\mu(\mathbb{1})\right)=\iota\left(1\right)=\left[1,1\right]$.
\item For any projection $P$, $\bar{\mu}\left(\mathbb{1}-P\right)=\iota\left(\mu(\mathbb{1}-P)\right)=\iota\left(1-\mu(P)\right)=\left[1,1\right]-\iota\left(\mu(P)\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$.
\item For a set of mutually orthogonal projections\nb$\left\{ P_{i}\right\} _{i=1}^{N}$,
we have $\sum_{i=1}^{N}\mu\left(P_{i}\right)=\mu\left(\sum_{i=1}^{N}P_{i}\right)\in\left[0,1\right]$
so that $\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)=\iota\left(\mu\left(\sum_{i=1}^{N}P_{i}\right)\right)=\iota\left(\sum_{i=1}^{N}\mu\left(P_{i}\right)\right)\subseteq\sum_{i=1}^{N}\iota\left(\mu\left(P_{i}\right)\right)=\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)$.
\item For convexity part, given a pair of commuting operators\nb$P_{0}$
and $P_{1}$, they and $P_{0}\vee P_{1}$ can be expressed by the
summation among $P_{0}\left(\mathbb{1}-P_{1}\right)$, $\left(\mathbb{1}-P_{0}\right)P_{1}$,
and $P_{0}P_{1}$. Hence, 
\begin{equation}\eqalign{ 
 & \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)=\iota\left(\mu\left(P_{0}\vee P_{1}\right)\right)+\iota\left(\mu\left(P_{0}P_{1}\right)\right)\\
= & \iota\left(\mu\left(P_{0}\left(\mathbb{1}-P_{1}\right)\right)+\mu\left(\left(\mathbb{1}-P_{0}\right)P_{1}\right)+\mu\left(P_{0}P_{1}\right)\right)+\iota\left(\mu\left(P_{0}P_{1}\right)\right)\\
\subseteq&\iota\left(\mu\left(P_{0}\left(\mathbb{1}-P_{1}\right)\right)+\mu\left(P_{0}P_{1}\right)\right)+\iota\left(\mu\left(\left(\mathbb{1}-P_{0}\right)P_{1}\right)+\mu\left(P_{0}P_{1}\right)\right)\\
= & \iota\left(\mu\left(P_{0}\right)\right)+\iota\left(\mu\left(P_{1}\right)\right)=\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right) 
}\end{equation}
\end{itemize}
\end{proof}

>>>>

Notice that the range of $\mu$ and $\bar{\mu}$ are different. If
there is a ``homomorphism''\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
preserving the desiring properties of the ranges, then we could easily
inducing a map from quantum real-valued probability measures to QIVPMs
by function composition\nb$\events\overset{\mu}{\rightarrow}\left[0,1\right]\overset{\iota}{\rightarrow}\mathscr{I}$.
This idea gives the following definition.

\begin{definition}We say a pair\nb$\left(\mathscr{I},\iota\right)$
is additive if $\mathscr{I}$ is a collection of intervals and $\iota:\left[0,1\right]\rightarrow\mathscr{I}$
is a function satisfying the following properties. 
\begin{itemize}
\item $\iota\left(0\right)=\left[0,0\right]$. 
\item $\iota\left(1\right)=\left[1,1\right]$. 
\item For any $x\in\left[0,1\right]$, $\iota\left(1-x\right)=\left[1,1\right]-\iota\left(x\right)$. 
\item For a set\nb$\left\{ x_{i}\right\} _{i=1}^{N}\subseteq\left[0,1\right]$,
if $\sum_{i=1}^{N}x_{i}\in\left[0,1\right]$, then $\iota\left(\sum_{i=1}^{N}x_{i}\right)\subseteq\sum_{i=1}^{N}\iota\left(x_{i}\right)$. 
\end{itemize}
Moreover, $\left(\mathscr{I},\iota\right)$ is called convex if for
any three numbers\nb$x_{0}$, $x_{1}$, and $x_{2}\in\left[0,1\right]$,
$x_{0}+x_{1}+x_{2}\in\left[0,1\right]$ implies $\iota\left(x_{0}+x_{1}+x_{2}\right)+\iota\left(x_{2}\right)\subseteq\iota\left(x_{0}+x_{2}\right)+\iota\left(x_{1}+x_{2}\right)$.\end{definition}

Although a convex pair\nb$\left(\mathscr{I},\iota\right)$ may look
exotic, the left end of $\iota$, defined by $\iotal\left(x\right)=\min\iota\left(x\right)$,
is well-studied Wright-convex satisfying $\iotal\left(x_{0}+x_{1}+x_{2}\right)+\iotal\left(x_{2}\right)\ge\iotal\left(x_{0}+x_{2}\right)+\iotal\left(x_{1}+x_{2}\right)$\nb\cite{Wright1954,RobertsVarberg1973,Pales2013}.
After we define\nb$\left(\mathscr{I},\iota\right)$, we are ready
to construct a QIVPM from a quantum probability measure.

@@

\begin{proof}~
\begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\iota\left(\mu(\mathbb{0})\right)=\iota\left(0\right)=\left[0,0\right]$.
\item $\bar{\mu}(\mathbb{1})=\iota\left(\mu(\mathbb{1})\right)=\iota\left(1\right)=\left[1,1\right]$.
\item For any projection $P$, $\bar{\mu}\left(\mathbb{1}-P\right)=\iota\left(1-\mu(P)\right)=\left[1,1\right]-\bar{\mu}\left(P\right)$.
\item For a set of mutually orthogonal projections\nb$\left\{ P_{i}\right\} _{i=1}^{N}$,
we have $\sum_{i=1}^{N}\mu\left(P_{i}\right)\in\left[0,1\right]$
so that $\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)=\iota\left(\sum_{i=1}^{N}\mu\left(P_{i}\right)\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)$.
\item For convexity part, given a pair of commuting operators\nb$P_{0}$
and $P_{1}$, they and $P_{0}\vee P_{1}$ can be expressed by the
summation among $P_{0}\left(\mathbb{1}-P_{1}\right)$, $\left(\mathbb{1}-P_{0}\right)P_{1}$,
and $P_{0}P_{1}$. Hence, 
\begin{equation}\eqalign{ 
 & \bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\\
= & \iota\left(\mu\left(P_{0}\left(\mathbb{1}-P_{1}\right)\right)+\mu\left(\left(\mathbb{1}-P_{0}\right)P_{1}\right)+\mu\left(P_{0}P_{1}\right)\right)+\iota\left(\mu\left(P_{0}P_{1}\right)\right)\\
\subseteq&\iota\left(\mu\left(P_{0}\left(\mathbb{1}-P_{1}\right)\right)+\mu\left(P_{0}P_{1}\right)\right)+\iota\left(\mu\left(\left(\mathbb{1}-P_{0}\right)P_{1}\right)+\mu\left(P_{0}P_{1}\right)\right)\\
= & \bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right) 
}\end{equation}
\end{itemize}
\end{proof}
